### 2019-04-29 manuscript.tex
Working with C; intermediate merge

It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{UNIC16}.  Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see \url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}  \cfonly{To rethink differences between FGC and FGM.  The types of FGC vary from just a knick to a sever sewing of the genital area.  Using FGC(cutting) seems to ignore the damage to the girls and human rights, but FGM(utilization) seem harsh and biased against local cultures.  FGC(cirumcision) may be the best for current situation globally.)

@@

The results of the three models are at ____.  The findings showed that all the three responses were clearly associated with the following predictors:  women’s fgc status, beliefs of fgc benefits and FGC prevalence in a community; so as the following factors:  country, media, education, age and religion and the community levels of media, education.  We did not find clear association of the community level of beliefs of fgc benefits and the three responses.

@@

- conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
- “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}. “alternative convention/peer convention\cite{ShelWand11}
 \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.  \cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}.  In \cite{MackLeJe08}, the authors saw marriageability was only one reason for FGC and proposed multiple factors in influencing women’s decision of cutting their daughters.

@@

- Beliefs of FGC benefits -
Our PCA results show that women’s beliefs of what benefits FGC brings is not clearly identified (see figure pca) and marriageability was not a clear one (to compare with \cite{Mack?,}.  On interpretation is that marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cite{EffeVogt15, MackLeJe08, ShelWand11, networking, part of social groups Duncan-Shell?}

@@

— Suggestions —
- empowering community, engaging community leaders and other strategies \citeBergDeni13b}
- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs. focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}
- modelling by plotting empirical data to study threshold/tipping point.
- redesign questions of fgc benefits in DHS
- inviting faced women migrated to western society to participate in fgc intervention campaign.  For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}

>>>>

It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{UNIC16}.  Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see \url{http://www.who.int/mediacentre/factsheets/fs241/en/} updated Sep, 18).  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}  \cfonly{To rethink differences between FGC and FGM.  The types of FGC vary from just a nick to a sever sewing of the genital area.  Using FGC(cutting) seems to ignore the damage to the girls and human rights, but FGM(utilization) seem harsh and biased against local cultures.  FGC(cirumcision) may be the best for current situation globally.}

@@

The results of the three models are at ???.  The findings showed that all the three responses were clearly associated with the following predictors:  women’s fgc status, beliefs of fgc benefits and FGC prevalence in a community; so as the following factors:  country, media, education, age and religion and the community levels of media, education.  We did not find clear association of the community level of beliefs of fgc benefits and the three responses.

@@

- conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
- “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}. “alternative convention/peer convention\cite{ShelWand11}
 \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.  \cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}.  In \cite{MackLeJe08}, the authors saw marriageability was only one reason for FGC and proposed multiple factors in influencing women’s decision of cutting their daughters.}

@@

- Beliefs of FGC benefits -
Our PCA results show that women’s beliefs of what benefits FGC brings is not clearly identified (see figure pca) and marriageability was not a clear one (to compare with \cite{Mack?,}.  On interpretation is that marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cfonly{Cite: EffeVogt15, MackLeJe08, ShelWand11, networking, part of social groups Duncan-Shell?}

@@

— Suggestions —
- empowering community, engaging community leaders and other strategies \cite{BergDeni13b}
- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs. focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}
- modelling by plotting empirical data to study threshold/tipping point.
- redesign questions of fgc benefits in DHS
- inviting faced women migrated to western society to participate in fgc intervention campaign.  For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}
